\documentclass[10pt]{article}
\usepackage{parskip}
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}
\usepackage{fontspec}

% Social icons
\usepackage{fontawesome5}

\RequirePackage{graphicx}

\RequirePackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[hidelinks, unicode, draft=falses]{hyperref}
\setmainfont{Arial}
\usepackage[normalem]{ulem}
\usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}
\usepackage{enumitem}

\begin{document}
\pagestyle{empty}

\newcolumntype{C}{>{\centering\arraybackslash}X}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Blain Weeks}
\\
{\underline{\href{mailto:blainweeks@icloud.com}{\raisebox{-0.05\height}{\faEnvelope} blainweeks@icloud.com}} $|$}
{\href{tel:+14843431779}{\raisebox{-0.05\height}{\faMobile} (484) 343-1779}}
\\
{\underline{\href{https://github.com/bweeks42}{\raisebox{-0.05\height}{\faGithub} GitHub}} $|$}
{\underline{\href{https://www.linkedin.com/in/blain-weeks-aba724119}{\raisebox{-0.05\height}{\faLinkedin} LinkedIn}} $|$}
{\underline{\href{https://www.blainweeks.com}{\raisebox{-0.05\height}{\faLink} Website}}}
\end{tabularx}

\section{Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{Apple}} \hfill \textit{November 2023 - Present}\\[4pt]
\textbf{\textit{Tools \& Automation Engineer}} \hfill \textit{Apple Pay} \\[5pt]
\begin{minipage}[t]{\linewidth}
\begin{itemize}[leftmargin=2em, nosep]%[nosep,after=\strut,leftmargin=2em, itemsep=2pt]
\item Just started :)
\end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{Capital One}} \hfill \textit{February 2022 - October 2023}\\[4pt]
\textbf{\textit{Senior Associate Software Engineer}} \hfill \textit{Card Tech} \\[5pt]
\begin{minipage}[t]{\linewidth}
\begin{itemize}[leftmargin=2em, nosep, after=\strut, itemsep=2pt]
\item Completed AWS Cloud Practitioner Certification.
\item Re-implemented virtual card number service to enable multi-threading.
\item Designed and implemented software to rotate PGP keys across a distributed system.
\item Served as production support engineer, resolving time-sensitive issues at all hours.
\item Contributed to the development of a new direct settlement application, utilizing AWS services such as Lambda, ECS and S3.
\item Helped manage a team of interns in the development of a tool to test application performance under load.
\end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{Apple}} \hfill \textit{July 2018 - February 2022}\\[4pt]
\textbf{\textit{Software Engineer}} \hfill \textit{Messages} \\[5pt]
\begin{minipage}[t]{\linewidth}
\begin{itemize}[leftmargin=2em, nosep, after=\strut, itemsep=2pt]
\item Contributed to Messages features, including Name and Photo Sharing, Spoken Messages and Child Safety.
\item Resolved issues at all levels of the Messages software stack, from data persistence to UI.
\item Implemented tools to automate running and reporting of unit tests at desk for team.
\item Developed automated testing suites to exercise the performance and functionality of various Messages features.
\item Wrote bug triage automation.
\item Implemented AppleScript hooks for Catalyst implementation of Messages app.
\item Worked cross-functionally with teams across Apple in design, security, performance, software and others.
\end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{AgilePQ}} \hfill \textit{September 2016 - June 2018}\\[4pt]
\textbf{\textit{Software Engineer}}\\[5pt]
\begin{minipage}[t]{\linewidth}
\begin{itemize}[leftmargin=2em, nosep, after=\strut, itemsep=2pt]
\item Integrated core security technology into Android and iOS platforms, as well as OpenVPN.
\item Developed cellular networking code for IoT devices.
\item Developed documentation using LaTeX for internal and customer use.
\item Met with customers to explain and demo mobile prototypes.
\item Developed automated suite to test network code.
\end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{AgilePQ}} \hfill \textit{June 2016 - Semptember 2016}\\[4pt]
\textbf{\textit{Software Engineering Intern}}\\[5pt]
\begin{minipage}[t]{\linewidth}
\begin{itemize}[leftmargin=2em, nosep, after=\strut, itemsep=2pt]
\item Developed communication protocols to establish secure communication between IoT devices and backend service.
\item Developed and tested network code for IoT devices.
\item Reviewed and provided feedback for technical portions of patent applications.
\end{itemize}
\end{minipage}
\end{tabularx}

\section{Education}
\textbf{California Polytechnic State University}, San Luis Obispo\\
\textit{B.S. in Software Engineering and Minor in Statistics} (2018)

\section{Expertise}
\begin{itemize}[leftmargin=2em, nosep, after=\strut, itemsep=2pt]
\item \textbf{Languages} - Swift, Python, Rust, C, Objective-C
\item \textbf{Technologies} - AWS, macOS, iOS
\item \textbf{Domains} - Application Development, Automated Testing
\end{itemize}


\end{document}

